Distinguishing multiple-merger from Kingman coalescence using two-site frequency spectra

### 2019-03-11 manuscript/manuscript.tex

\title{Distinguishing multiple-merger from Kingman coalescence using two-site frequency spectra}
\author[1,2]{Daniel P. Rice}
\author[1,2,*]{John Novembre}
\author[3,4,*]{Michael M. Desai}
\affil[1]{Department of Human Genetics, University of Chicago, Chicago, IL}
\affil[2]{Department of Ecology and Evolution, University of Chicago, Chicago, IL}
\affil[3]{Department of Organismic and Evolutionary Biology, Harvard University, Cambridge, MA}
\affil[4]{Department of Physics, Harvard University, Cambridge, MA}
\affil[*]{These authors contributed equally to this work.}
\date{\today}

@@

>>>>

\title{Distinguishing multiple-merger from Kingman coalescence using two-site frequency spectra}
\author[$\ast$,$\dagger$,1]{Daniel P. Rice}
\author[$\ast$,$\dagger$,2]{John Novembre}
\author[$\ddager$,$\S$,2]{Michael M. Desai}
\affil[$\ast$]{Department of Human Genetics, University of Chicago, Chicago, IL}
\affil[$\dagger$]{Department of Ecology and Evolution, University of Chicago, Chicago, IL}
\affil[$\ddager$]{Department of Organismic and Evolutionary Biology, Harvard University, Cambridge, MA}
\affil[$\S$]{Department of Physics, Harvard University, Cambridge, MA}
\affil[1]{Corresponding author: 920 E 58th St, Chicago, IL 60637, \url{dpr@uchicago.edu}}
\affil[2]{These authors contributed equally to this work.}
\date{\today}

@@

\textbf{Keywords:} multiple-mergers coalescent, demographic inference, model checking, site frequency spectrum, mutual information

\textbf{Short Title:} Detecting multiple mergers using 2-SFS
